\subsubsection{Random Numbers}\label{sec:Services_RAND}

A Random Number service is provided, with the gsl Random Number Generator encapsulated in a singleton object (an instantiation of the Rand class).  

The Rand class member variables are private, and public functions have been created for random number functionality required by the code.

The Rand service can be accessed by referring to the Rand::Instance() object.  For example, to generate a uniform random floating point number in the range [0, 1), call the Random() function:

\tabto{3em}double u = Rand::Instance()\rarr{Random();}

\medskip
Since that could become unwieldy, there is a convenience macro to access the Rand service.  The macro just defines "RAND" as "Rand::Instance()", so calling the Random() function can be written as:

\tabto{3em}double u = RAND\rarr{Random();}

\medskip
The Rand service must be initialised before use.  Initialise the Rand service by calling the Initialise() function:

\tabto{3em}RAND\rarr{Initialise();}

\medskip
Dynamically allocated memory associated with the gsl random number generator should be returned to the system by calling the Free() function:

\tabto{3em}RAND\rarr{Free();}

before exiting the program.

\bigskip
The Rand service provides the following public member functions:

\hfill
\begin{minipage}{\dimexpr\textwidth-3em}
    \bigskip\textbf{void Initialise()}

    Initialises the gsl random number generator.  If the environment variable GSL\_RNG\_SEED exists, the gsl random number generator is seeded with the value of the environment variable, otherwise it is seeded with the current time.

    \bigskip\textbf{void Free()}

    Frees any dynamically allocated memory.

    \bigskip\textbf{unsigned long int Seed(const unsigned long p\_Seed)}

    Sets the seed for the gsl random number generator to p\_Seed.  The return value is the seed.

    \bigskip\textbf{unsigned long int DefaultSeed()}

    Returns the gsl default seed (gsl\_rng\_default\_seed)

    \bigskip\textbf{double Random(void)}

    Returns a random floating point number uniformly distributed in the range [0.0, 1.0)

    \bigskip\textbf{double Random(const double p\_Lower, const double p\_Upper)}

    Returns a random floating point number uniformly distributed in the range [p\_Lower, p\_Upper), where p\_Lower $\leq$ p\_Upper.

    (p\_Lower and p\_Upper will be swapped if p\_Lower $\mathrm{>}$ p\_Upper as passed)
\end{minipage}

\hfill
\begin{minipage}{\dimexpr\textwidth-3em}
    \bigskip\textbf{double RandomGaussian(const double p\_Sigma)}

    Returns a Gaussian random variate, with mean 0.0 and standard deviation p\_Sigma

    \bigskip\textbf{int RandomInt(const int p\_Lower, const int p\_Upper)}

    Returns a random integer number uniformly distributed in the range [p\_Lower, p\_Upper), where p\_Lower $\leq$ p\_Upper.

    (p\_Lower and p\_Upper will be swapped if p\_Lower $>$ p\_Upper as passed)

    \bigskip\textbf{int RandomInt(const int p\_Upper)}
    Returns a random integer number uniformly distributed in the range [0, p\_Upper),where 0 $\leq$ p\_Upper.  Returns 0 if p\_Upper $<$ 0.
\end{minipage}