\subsection{Object Identifiers}\label{sec:ObjectIdentifiers}

All objects (instantiations of a class) are assigned unique object identifiers of type OBJECT\_ID (unsigned long int - see \nobreak{\textbf{constants.h}} for the typedef).  The purpose of the unique object id is to aid in object tracking and debugging.

Note that the object id is not the same as, nor does it supersede, the RANDOM SEED value assigned to each single or binary star. The RANDOM SEED is used to seed the random number generator, and can be used to uniquely identify a single or binary star. The object id is more granular the the RANDOM SEED. Each binary star is comprised of multiple objects: the BinaryStar object, which contains two BaseBinaryStar objects (the object undergoing evolution, and a saved copy); each BaseBinaryStar object contains two BinaryConstituentStar objects (one for each of the constituent stars), and each BinaryConstituentStar object inherits from the Star class, which contains two BaseStar objects (the underlying star and a saved copy). Whereas the RANDOM SEED uniquely identifies (for example) a binary star, and so identifies the collection of objects that comprise the binary star, the object ids uniquely identify the constituent objects of the binary star.

% could put a linebreak here to fix the 'Overfull \hbox' warning, but probably no need
As well as unique object ids, all objects are assigned an object type (of type OBJECT\_TYPE -- see \nobreak{\textbf{constants.h}} for the enum class declaring OBJECT\_TYPE), and a stellar type where applicable (of type STELLAR\_TYPE -- see \nobreak{\textbf{constants.h}} for the enum class declaring STELLAR\_TYPE).

Objects should expose the following functions:

\tabto{3em}OBJECT\_ID  ObjectId() const \lcb\ return m\_ObjectId;\ \rcb \\
\tabto{3em}OBJECT\_TYPE ObjectType() const \lcb\ return m\_ObjectType;\ \rcb \\
\tabto{3em}STELLAR\_TYPE StellarType() const \lcb\ return m\_StellarType;\ \rcb

If any of the functions are not applicable to the object, then they must return "*::NONE" (all objects should implement ObjectId() correctly).

Any object that uses the Errors service (i.e. the SHOW\_* macros) \textit{\underbar{must}} expose these functions: the functions are called by the SHOW\_* macros (the Errors service is described later in this document).
